---
title: DE LOS DATOS A LA ACCIÓN:Shiny como herramienta para la divulgación y el cambio social
author: Maria Monserrat Perez Villanueva, Jorge Ruiz Reyes & Alicia Valentina Franco Boscan
date: "`r Sys.Date()`"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE, include=TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


## Responsive slide 1

- Exhibir el problema



## Responsive slide 2

- Clases de utilidad de bootstrap --> agilizan el desarrollo web
- Ayuda a diseñar rápidamente elementos sin usar código CSS
- Clases que cruzan breakpoints y propiedades de diseño


## Solución usando bootsrap

```{html, echo = T, eval = F}
<div class="row d-flex">
    <div class = “graph-container col-sm-12 col-md-8 align-items-center position mb-lg-3”>
        ...
    <div/>
    <div class = “text-container col-sm-12 col-md-3 my-auto mx-auto”>
		  ...
    <div/>
<div/>

```


## ¿Cuál era la alternativa?

-Generar un un html y css con layout y tamaños de mobile
-Adicionalmente agregar media queries para


## Solucion con media queries

```{css, echo = T, eval = F}

@media (min-width: 768 px) {

.graph-container{
            flex: 0 0 auto;
            width: 66.66667 %;
            }

.text-container{
            flex: 0 0 auto;
            width:25%;
            }
}
```


## Otra






